Blueprint for efficient nuclear spin characterization with color center

### 2024-05-18 PRB - revision reply/reply.tex
iteration finished

	2. $T_1$ limits the resolution of the frequency spectrum. However, $T_2$ limits the weakest nuclear spin that can be addressed. Ideally, by increasing number of $\pi$ pulses, this limit can be pushed toward $T_1$. (did we mention this in the text?) While short transverse relaxation time tolerable, having short longitudinal relaxation time basically means that nuclear spin is not a desired quantum memory. \\

	3. Using correlation sequences as quantum gates can be challenging as they are not unitary gates due to transverse relaxation of the spins.\\

>>>>

	2. $T_1$ limits the resolution of the frequency spectrum. However, $T_2$ defines the sensitivity to the weakest nuclear spin that can be addressed. Ideally, by increasing number of $\pi$ pulses, this limit can be pushed toward $T_1$. While short transverse relaxation time tolerable, having short longitudinal relaxation time basically means that the system is not suitable for consideration as a desired quantum memory. \\

	3. Using correlation sequences as quantum gates can be challenging as they are not unitary gates due to transverse relaxation of the spins. However the protection of the central spin during the correlation time $T_c$ or purification of the gate by a heralded projection at the end of the sequence opens the possibility to use them as a gate and requires further investigation.\\
